Inferring probabilistic stellar rotation periods using Gaussian processes

### 2017-02-05 documents/ms.tex
ls section edits

For each simulated light curve, a LS periodogram
\footnote{LS periodograms were calculated using the gatspy Python module:
\url{https://github.com/astroML/gatspy/tree/master/gatspy/periodic}.}
was computed over a grid of 10,000 periods, evenly spaced in frequency,
between 1 and 100 days.
The period of the highest peak in the periodogram was adopted as the rotation
period.
The resulting recovered rotation periods are plotted as a function of the true
periods in figure \ref{fig:pgram_compare}.
The MRD of the pgram-recovered periods is \percentpgramMAD\% (see table
\ref{tab:MADs} for a side-by-side comparison with the other methods).
There is a large number of drastically overestimated periods recovered using
the periodogram.
Excess power at long periods can be generated by long-term trends that are not
related to rotation.
This problem becomes exacerbated when instrumental noise is also present in
light curves.

>>>>

For each simulated light curve, we compute a LS periodogram
\footnote{LS periodograms were calculated using the gatspy Python module:
\url{https://github.com/astroML/gatspy/tree/master/gatspy/periodic}.}
over a grid of 10,000 periods, evenly spaced in frequency,
between 1 and 100 days.
We adopt the period of the highest peak in the periodogram as the rotation
period.
Figure \ref{fig:pgram_compare} shows the resulting recovered rotation periods
as a function of true period.
The MRD of the periodogram-recovered periods is \percentpgramMAD\% (see table
\ref{tab:MADs} for a side-by-side comparison with the other methods).
This method drastically overestimates many rotation periods, 
because long-term trends unrelated to rotation can cause excess power
at long periods---a problem further exacerbated by instrumental noise. 
\tdmcomment{I don't quite understand this---what do we mean here by 
``instrumental noise'' as distinct from long-term trends?}
